R Notebook

### 2024-05-14 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
    # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

@@

@@

>>>>

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
    # filter(time <= 600) %>% # filter for 10min intervals
    # filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

@@

## count for individuals 
main %>% 
  filter(time >= 7200) %>% 
  distinct(ID, .keep_all = TRUE) -> filter_overall

@@

## age x teaching experience
``` {r}
main %>% 
  filter(time_span == "overall") %>% 
  group_by(ID) %>% 
  select(ID,
         teaching_experience,
         age) -> teach_gender

cor(cor_teach_gender$teaching_experience,
    cor_teach_gender$age,
    method = c("pearson")
  ) -> cor_teach_gender
